---
title: "Data Structure and a Naive Model"
author: "Zeyi Wang"
date: "September 20, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = "..")
```

## 0. Quantitative question

- Can we design a self-driving car?

- Can we predict the appropriate acceleration and steering angle based on data collected by the camera and GPS, such as speed, acceleration, steering angle and camera images?

## 1. Data Structure

45 GB compressed, 80 GB uncompressed (unzip it in Windows 10, not Mac OS)

```{r list.files}
list.files(file.path("comma-dataset"), recursive = T)
```

We will need 'h5' package to extract data from *.h5 files. 

```{r h5 package}
library("h5")
log <- H5File(file.path("comma-dataset", "log", "2016-06-08--11-46-01.h5"))
image <- H5File(file.path("comma-dataset", "camera", "2016-06-08--11-46-01.h5"))
log_names <- list.datasets(log, recursive = TRUE)
image_names <- list.datasets(image, recursive = TRUE)
```

So the function insists that I am deprecating it. Well. 

### 1.1 Image Data

The image part are pixel images, 20 pic per sec, 320*160 pixels per pic, with RGB format. 

```{r}
image[image_names]  #check the image we loaded
```

So the dimension is **Frames * RGB * Columns * Rows**. 

Image data are basically **4 d arrays**.

```{r}
range(image[image_names][1,,,])
```

The values coincide with RGB format. 

Actually why don't we check some of the images:

```{r, message=FALSE}
library(imager)
par(mfrow = c(2, 2))  
plot(as.cimg(aperm(image[image_names][10001,,,], c(4,3,1,2))))  #the start of training set
plot(as.cimg(aperm(image[image_names][13001,,,], c(4,3,1,2))))  #the end of training set
plot(as.cimg(aperm(image[image_names][14002,,,], c(4,3,1,2))))  #the start of test set
plot(as.cimg(aperm(image[image_names][15002,,,], c(4,3,1,2))))  #the end of test set
par(mfrow = c(1, 1))  
```

Difficulties to overcome:

Sometimes the roads are with lines while sometimes they don't; 

It could be a truck but it also could be the shadow (cars in the same direction do stay longer though). 

### 1.2 Log Data

reference: [link to comma.ai github](https://github.com/commaai/research/blob/master/Logs.md)

The log files are with the same names, but under the "./comma-dataset/log/" folder. 

Let's check the first hierachy of the log: 

```{r}
log_names
```

There are speed[28], acceleration[14], steering angle[35], steering torque[36]. 

####Check the speed first:

```{r speed}
temp <- log[log_names[28]]@dim
speed <- log[log_names[28]][1:temp]
rm(temp)
hist(speed)
```

####Acceleration: 

```{r accel}
temp <- log[log_names[14]]@dim
accel <- log[log_names[14]][1:temp]
rm(temp)
range(accel)
hist(accel, breaks = 100)
```

Most of the time, the car keeps its speed;

```{r  accel cont}
sum(accel > 0.8)
sum(accel < -0.8)
length(accel)
accel_tri <- 1 * (accel > 0.8) - 1 * (accel < - 0.8)  #this is the "answer" for supervised learning
```

It would be great if we can first of all predict accelerating/slowing down/keeping speed status. 

####Steering:

```{r steering}
library(scales)

temp <- log[log_names[35]]@dim
angle <- log[log_names[35]][1:temp]
rm(temp)
angle <- scale(angle)
temp <- log[log_names[36]]@dim
angle_accel <- log[log_names[36]][1:temp]
rm(temp)
angle_accel <- rescale(angle_accel, to = c(-1, 1))

hist(angle)
hist(angle_accel)
```

It would help the training that we scale the variables. 

### 1.3 Timeline

The "/cam1_ptr" in log file records the timeline. 

```{r timeline}
temp <- log[log_names[13]]@dim
timeline_image <- log[log_names[13]][1:temp]
rm(temp)
length(timeline_image)
range(timeline_image)
```

Simple calculation: 

There are 90870 time points in log, 18176 time points in image; 

100Hz for log; 20Hz for image; 

90870/100 = 18176/20 = 908.8 sec = 15.1 min; 

It is the shortest driving set. 


## 2. A Naive Model

We will predict acceleration status, but we won't use image for now. 

So it is a helpful warmup for convolutional network training. 

```{r accel_tri}
hist(accel_tri)
```

#### The naive model:    
**Acceleration status** ~ 10sec **speed** + 10sec **steering angle** + 10sec **angle acceleration**
    
### 2.1 Training, Validation and Testing set

```{r}
set.seed(160920)
index_train <- sample(50001:65000, size = 10000)
index_validation <- setdiff(50001:65000, index_train)
index_test <- 70001:75000

set_train <- matrix(0, 10000, 31)
set_train[,1] <- as.matrix(accel_tri[index_train])
for (i in 1:10) {
    set_train[,i + 1] <- speed[index_train-i*100]
    set_train[,i + 11] <- angle[index_train-i*100]
    set_train[,i + 21] <- angle_accel[index_train-i*100]
}


set_validation <- matrix(0, 5000, 31)
set_validation[,1] <- as.matrix(accel_tri[index_validation])
for (i in 1:10) {
    set_validation[,i + 1] <- speed[index_validation-i*100]
    set_validation[,i + 11] <- angle[index_validation-i*100]
    set_validation[,i + 21] <- angle_accel[index_validation-i*100]
}

set_test <- matrix(0, 5000, 31)
set_test[,1] <- as.matrix(accel_tri[index_test])
for (i in 1:10) {
    set_test[,i + 1] <- speed[index_test-i*100]
    set_test[,i + 11] <- angle[index_test-i*100]
    set_test[,i + 21] <- angle_accel[index_test-i*100]
}
```

### 2.2 Fitting with random forests

```{r, message=FALSE}
library(randomForest)
model_naive <- randomForest(set_train[,2:31], as.factor(set_train[,1]))

sum(predict(model_naive, set_validation[,2:31]) == set_validation[,1])/5000  #validation
sum(predict(model_naive, set_test[,2:31]) == set_test[,1])/5000  #test
```

The validation set is contaminated. 

```{r}
sum(predict(model_naive, set_test[set_test[,1] == 0 ,2:31]) == set_test[set_test[,1] == 0 ,1])/sum(set_test[,1] == 0)
sum(predict(model_naive, set_test[set_test[,1] == 1 ,2:31]) == set_test[set_test[,1] == 1 ,1])/sum(set_test[,1] == 1)
sum(predict(model_naive, set_test[set_test[,1] == -1 ,2:31]) == set_test[set_test[,1] == -1 ,1])/sum(set_test[,1] == -1)
```

So we can see that the image data is needed. 

## 3. Plan this week

The project is difficult in two meanings: 

    - We need to deal with image data;
    - Convolutional learning is always difficult.
    
In addition, we will need to predict acceleration and steering angle in the end. 
    
#### Tasks:

- Example codes for angle prediction; visualizing the results

- Simple ideas for image data: stamping out by grid regions; outlier detection

- Papers regarding convolutional learning

- A slightly improved model with images involved

```{r}
M <- aperm(image[image_names][13001,,,], c(4,3,1,2))
MM <- M[,,1,1]>=235
MMM <- M
for (i in 1:3) {
    MMM[,,1,i] <- MM*M[,,1,i]
}
plot(as.cimg(MMM))
plot(as.cimg(M))
```